R Python, and Ruby clients for GBIF species occurrence data

### 2017-09-23 use-cases/niche-modelling.Rmd
need possibly pkg sp in niche modelling use case
install pkg sp first in niche modelling use case
spelling

In this example, we plot actual occurrence data for _Bradypus_ species against a single predictor variable, BIO1 (annual mean temperature). This is only ont step in a species distribution modelling nworkflow.

@@

```{r}
library("rgbif")
library("dismo")
library("maptools")
library("plyr")
```

@@

```{r cache=TRUE}
nn <- name_lookup("bradypus*", rank = "species")
nn <- na.omit(unique(nn$data$nubKey))
df <- occ_search(taxonKey = nn, hasCoordinate = TRUE, limit = 500)
df <- df[ sapply(df, function(x) class(x$data)) %in% "data.frame" ]
df <- ldply(lapply(df, "[[", "data"))
df2 <- df[,c('decimalLongitude','decimalLatitude')]
```

>>>>

In this example, we plot actual occurrence data for _Bradypus_ species against a single predictor variable, BIO1 (annual mean temperature). This is only one step in a species distribution modelling workflow.

@@

```{r}
library("sp")
library("rgbif")
library("dismo")
library("maptools")
library("dplyr")
```

@@

```{r cache=FALSE}
nn <- name_lookup("bradypus*", rank = "species")
nn <- na.omit(unique(nn$data$nubKey))
df <- occ_search(taxonKey = nn, hasCoordinate = TRUE, limit = 500)
df_data <- df[ sapply(df, function(x) any(class(x$data) %in% "tbl_df")) ]
df_data <- dplyr::bind_rows(lapply(df_data, "[[", "data"))
df2 <- df_data %>% dplyr::select(decimalLongitude, decimalLatitude)
```
